Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis

### 2018-02-16 manuscript/02_methods.Rmd
Revise formatting for submission

We assigned each species to a unique plant functional type (PFT) following the scheme in the Community Land Model [CLM4.5, @clm45_note; Tab.\ \@ref(tab:pfts), Fig.\ 1].
We obtained categorical data on growth form, leaf type, phenology, and photosynthetic pathway from the TRY database.
Where species attributes disagreed between datasets (e.g., categorized as a shrub in one dataset but a tree in another), we assigned the attribute that was observed most frequently between the datasets (e.g., if five datasets say "shrub" but only one says "tree", we would classify it as a shrub).
Where species lacked data on certain attributes, we assigned those attributes based on higher order phylogeny where appropriate (e.g., \em{Poaceae} family are usually grasses, \em{Larix spp.} are deciduous needleleaved trees) or otherwise omitted the species from our analyses.
For biome specification, we collected all latitude and longitude data for each species,
matched these data to 30 second ($\sim1$ km$^{2}$) mean annual temperature ($AMT$, averaged 1970-2000) data from WorldClim-2 [@worldclim],
calculated the mean AMT for all sites at which that species was observed,
and then binned these species based on the following cutoffs: boreal/arctic ($AMT \leq 5^\circ C$), temperate ($AMT \leq 20^\circ C$), and tropical ($AMT > 20^\circ C$).

>>>>

We assigned each species to a unique plant functional type (PFT) following the scheme in the Community Land Model [CLM4.5, @clm45_note; Tab.\ \@ref(tab:pfts), Fig.\ 1].
We obtained categorical data on growth form, leaf type, phenology, and photosynthetic pathway from the TRY database.
Where species attributes disagreed between datasets (e.g., categorized as a shrub in one dataset but a tree in another), we assigned the attribute that was observed most frequently between the datasets (e.g., if five datasets say "shrub" but only one says "tree", we would classify it as a shrub).
Where species lacked data on certain attributes, we assigned those attributes based on higher order phylogeny where appropriate (e.g., *Poaceae* family are usually grasses, *Larix spp.* are deciduous needleleaved trees) or otherwise omitted the species from our analyses.
For biome specification, we collected all latitude and longitude data for each species,
matched these data to 30 second ($\sim1$ km$^{2}$) mean annual temperature ($AMT$, averaged 1970-2000) data from WorldClim-2 [@worldclim],
calculated the mean AMT for all sites at which that species was observed,
and then binned these species based on the following cutoffs: boreal/arctic ($AMT \leq 5^\circ C$), temperate ($AMT \leq 20^\circ C$), and tropical ($AMT > 20^\circ C$).

### 2018-02-16 manuscript/index.Rmd
Revise formatting for submission

---
title: "Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis"
author:
  - >
    Alexey N. Shiklomanov$^1$
    Elizabeth M. Cowdery$^1$,
    Michael Bahn$^2$,
    Chaeho Byun$^3$,
    Joseph Craine$^4$,
    Andrés Gonzalez-Melo$^5$,
    Alvaro G. Gutiérrez$^6$,
    Steven Jansen$^7$,
    Nathan Kraft$^8$,
    Koen Kramer$^{9}$,
    Vanessa Minden$^{10,11}$,
    Ülo Niinemets$^{12}$,
    Yusuke Onoda$^{13}$,
    Enio Egon Sosinski$^{14}$,
    Nadejda A. Soudzilovskaia$^{15}$,
    Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::word_document2:
    toc: no
    reference_docx: ~/Projects/misc/pandoc-docx-template/academic-numbered.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
<div custom-style="Affiliation">
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
</div>

@@

```{r wordcount, echo = FALSE}
fnames <- c(
  introduction = "01_introduction.md",
  methods = "02_methods.Rmd",
  results = "03_results.Rmd",
  discussion = "04_discussion.md",
  conclusions = "05_conclusions.md"
)
files <- here::here(
  "manuscript", 
  fnames
)
names(files) <- names(fnames)

@@

# Summary {-}

>>>>

---
title: "Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis"
author:
  - >
    Alexey N. Shiklomanov$^1$
    Elizabeth M. Cowdery$^1$,
    Michael Bahn$^2$,
    Chaeho Byun$^3$,
    Joseph Craine$^4$,
    Andrés Gonzalez-Melo$^5$,
    Alvaro G. Gutiérrez$^6$,
    Steven Jansen$^7$,
    Nathan Kraft$^8$,
    Koen Kramer$^{9}$,
    Vanessa Minden$^{10,11}$,
    Ülo Niinemets$^{12}$,
    Yusuke Onoda$^{13}$,
    Enio Egon Sosinski$^{14}$,
    Nadejda A. Soudzilovskaia$^{15}$,
    Michael C. Dietze$^1$
bibliography:
  - library.bib
  - extra.bib
  - tryrefs.bib
csl: new-phytologist.csl
output:
  bookdown::word_document2:
    toc: no
    reference_docx: ~/Projects/misc/pandoc-docx-template/custom.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    includes:
      in_header: preamble.tex
---
<div custom-style="Affiliation">
$^1$Department of Earth & Environment, Boston University, Boston, MA 02215, USA;
$^2$Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria;
$^3$School of Biological Sciences, Seoul National University, Gwanak-ro 1, 08826, Seoul, Seoul, South Korea;
$^4$Jonah Ventures, Manhattan, KS 66502, USA;
$^5$Universidad del Rosario. Facultad de Ciencias Naturales y Matemáticas. Carrera 26 #63B-48. Bogotá, Colombia;
$^6$Departamento de Ciencias Ambientales y Recursos Naturales, Facultad de Ciencias Agronomicas, Universidad de Chile, Av. Santa Rosa 11315, La Pintana 8820808, Santiago, Chile;
$^7$Institute of Systematic Botany and Ecology, Ulm University, Ulm, Germany;
$^8$Department of Ecology and Evolutionary Biology, University of California Los Angeles, Los Angeles, CA 90095, USA;
$^{9}$Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands;
$^{10}$Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany;
$^{11}$Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels;
$^{12}$Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia;
$^{13}$Graduate School of Agriculture, Kyoto University, Kyoto, 606-8502, Japan;
$^{14}$Embrapa Temperate Agriculture, Rodovia BR 392, Km 78, CEP 96010-971 Pelotas, RS, Brazil;
$^{15}$Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands
</div>

@@

```{r wordcount, echo = FALSE}
fnames <- c(
  introduction = "01_introduction.md",
  methods = "02_methods.Rmd",
  results = "03_results.Rmd",
  discussion = "04_discussion.md"
)
files <- here::here(
  "manuscript", 
  fnames
)
names(files) <- names(fnames)

@@

<div custom-style="Heading, no number">Summary</div>
